Homework 8

### 2019-11-05 hw8/MSimonsHW8.tex
hw8 problem 2a
hw8 prob 3

@@

>>>>

\item
\begin{enumerate}
\item
Let $f(x) = x^3 + 2x + 1$.  We know that $f(x)$ is irreducible in
$\mathbb{Z}/3\mathbb{Z}$ because $f(0) = f(1) = f(2) = 1$.  Therefore,
$K$ is a field.

@@

\item To prove that $(a,b) = (d)$, first let us prove that $(a,b) \subseteq (d)$.
Let $ar_1 + br_2$ be any element of $(a,b)$.  Since $d$ is the greatest common
divisor of $a$ and $b$, $a = dx$ and $b = dy$ for some integers $x$ and $y$.
Therefore, $ar_1 + br_2 = dxr_1 + dyr_2 = d(xr_{1} + dyr_{2})$, which is an
element of $(d)$.  Thus, $(a,b) \subseteq (d)$. \\ \\
Next, let us prove $(d) \subseteq (a,b)$.  Since $d$ is the greatest common
divisor of $a$ and $b$, $d = au + bv$ for some integers $u$ and $v$.  Let
$rd$ be any element of $(d)$.
Therefore, $rd = r(au + bv) = rau + rbv = a(ru) + b(rv) \subseteq (a,b)$.
Thus $(d) \subseteq (a,b)$. \\ \\
Since $(d) \subseteq (a,b)$ and $(a,b) \subseteq (d)$, $(a,b) = (d)$.
